Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2022-03-14 Edith Zemanick/Sweat Test/sweat_test_analysis.Rmd
Update sweat_test_analysis.Rmd

```{r}
# Write groups of interest
write.csv(df %>% filter(Diagnosis == "Non-CF",Cl >= 60),na = "",
          file = "./Data_Cleaned/non_cf_cl_over_60.csv",row.names = F)
write.csv(df %>% filter(Diagnosis == "Cystic Fibrosis",Cl < 60),na = "",
          file = "./Data_Cleaned/cf_cl_under_60.csv",row.names = F)
write.csv(df %>% filter(Diagnosis == "Cystic Fibrosis",Cl >= 30 & Cl < 60),na = "",
          file = "./Data_Cleaned/cf_cl_30_59.csv",row.names = F)
```

>>>>

```{r}
# Write groups of interest
write.csv(df %>% filter(Diagnosis == "Non-CF",Cl >= 60),na = "",
          file = "./Data_Cleaned/non_cf_cl_over_60.csv",row.names = F)
write.csv(df %>% filter(Diagnosis == "Non-CF",Cl >= 30 & Cl < 60),na = "",
          file = "./Data_Cleaned/non_cf_cl_30_59.csv",row.names = F)
write.csv(df %>% filter(Diagnosis == "Cystic Fibrosis",Cl < 60),na = "",
          file = "./Data_Cleaned/cf_cl_under_60.csv",row.names = F)
write.csv(df %>% filter(Diagnosis == "Cystic Fibrosis",Cl >= 30 & Cl < 60),na = "",
          file = "./Data_Cleaned/cf_cl_30_59.csv",row.names = F)
```
